Asymmetric relationships and their effects on coexistence

### 2023-06-29 paper/Paper.Rnw
trivial

#place R code here for loading in necessary variables from Results
res_loc <- "../results_numeric/"
#fig2 <- readRDS(file=paste0(res_loc,"fig2data.RDS"))
M <- readRDS(file=paste0(res_loc,"M.RDS"))
se3 <- readRDS(file=paste0(res_loc,"fig3maxse.RDS"))
se4 <- readRDS(file=paste0(res_loc,"fig4maxse.RDS"))
se5 <- 1 #readRDS(file=paste0(res_loc, "fig5maxse.RDS"))
#se6 <- readRDS(file=paste0(res_loc, "fig6maxse.RDS"))
@

@@

\noindent \textbf{Running head:} Asymmetric relationships and coexistence \\
\noindent \textbf{Key words:} asymmetric tail association, biodiversity, coexistence, competition, copula, modern coexistence theory, niche differentiation, storage effects \\
\noindent \textbf{Type of article:} Letter\\
\noindent \textbf{Words in Abstract:} 150; \textbf{Words in main text:} 5013; \textbf{Words in text boxes:} 0\\
\noindent \textbf{Number of references:} 39; \textbf{Number of figures:} 4; \textbf{Number of tables:} 1; \textbf{Number of text boxes:} 0\\
\noindent \textbf{Corresponding author:}
Daniel C. Reuman,
Department of Ecology and Evolutionary Biology,
University of Kansas,
2101 Constant Ave,
Lawrence, KS 66047;
Phone: 626-560-7084 \\
\noindent \textbf{Author emails:} pimsupaa@uoregon.edu, reuman@ku.edu\\
\noindent \textbf{Statement of Authorship:} The authors jointly carried out all parts of the study.\\
\noindent \textbf{Data accessibility statement:} All codes associated with this study will be released
in a Zenodo repository prior to publication.

>>>>

#place R code here for loading in necessary variables from Results
res_loc <- "../results_numeric/"
#fig2 <- readRDS(file=paste0(res_loc,"fig2data.RDS"))
M <- readRDS(file=paste0(res_loc,"M.RDS"))
se3 <- readRDS(file=paste0(res_loc,"fig3maxse.RDS"))
se4 <- readRDS(file=paste0(res_loc,"fig4maxse.RDS"))
se5 <- readRDS(file=paste0(res_loc, "fig5maxse.RDS"))
#se6 <- readRDS(file=paste0(res_loc, "fig6maxse.RDS"))
@

@@

\noindent \textbf{Running head:} Asymmetric relationships and coexistence \\
\noindent \textbf{Key words:} asymmetric tail association, biodiversity, coexistence, competition, copula, modern coexistence theory, niche differentiation, storage effects \\
\noindent \textbf{Type of article:} Letter\\
\noindent \textbf{Words in Abstract:} 150; \textbf{Words in main text:} 5013; \textbf{Words in text boxes:} 0\\
\noindent \textbf{Number of references:} 37; \textbf{Number of figures:} 4; \textbf{Number of tables:} 1; \textbf{Number of text boxes:} 0\\
\noindent \textbf{Corresponding author:}
Daniel C. Reuman,
Department of Ecology and Evolutionary Biology,
University of Kansas,
2101 Constant Ave,
Lawrence, KS 66047;
Phone: 626-560-7084 \\
\noindent \textbf{Author emails:} pimsupaa@uoregon.edu, reuman@ku.edu\\
\noindent \textbf{Statement of Authorship:} The authors jointly carried out all parts of the study.\\
\noindent \textbf{Data accessibility statement:} All codes associated with this study will be released
in a Zenodo repository prior to publication.
